Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-16 resex.tex
Revised results on random excitation, including figures.

\begin{figure*}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		no excitation
		\includegraphics[width=1.0\linewidth]{2017injnocolc15o+19_6noerru_dp0_amp.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		uniform random H+V
		\includegraphics[width=1.0\linewidth]{2017injnocolc15o+19_6noerruranadthv_1nrad_dp0_amp.png}
	\end{minipage}	
	\caption{\label{fig:ran2017fmaamp} FMA analysis in amplitude space without excitation (left) and for a uniform random excitation with 1~nrad amplitude (right) in H+V based on the 2017 injection optics with no machine errors and a tune of (62.27,60.295).}
\end{figure*}

\begin{figure*}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2u_ranadt_3_5um_intensity.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2u_ranadt_3_5um_sigm.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2u_ranadt_3_5um_emit1.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2u_ranadt_3_5um_emit2.png}
	\end{minipage}
	\caption{\label{fig:ransim} Relative intensity (top left), bunch length (top right), and horizontal (bottom left) and vertical (bottom right) emittance obtained from distribution tracking based on the 2017 injection optics with standard lattice errors and $(Q_x,Q_y)=(62.27,60.295)$. The solid line indicates the case with no excitation, and the dotted and dashed line the results for a uniform random excitation of 12~nrad and 24~nrad respectively.}
      \end{figure*}

\begin{figure*}
	random excitation V\\
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[height=0.75\linewidth]{2017_bunch_intensity_vran_no_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[height=0.75\linewidth]{2017_emith_avg_rel_vran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[height=0.75\linewidth]{2017_emitv_avg_rel_vran_no_damper.png}
	\end{minipage}	
		random excitation H+V\\
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[height=0.75\linewidth]{2017_bunch_intensity_hvran_no_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[height=0.75\linewidth]{2017_emith_avg_rel_hvran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[height=0.75\linewidth]{2017_emitv_avg_rel_hvran_no_damper.png}
	\end{minipage}	
	\caption{\label{fig:ranexp} Relative intensity (left) and relative horizontal (center) and vertical (right) emittance for a random excitation only in V (top) and in H+V (bottom). Emittance growth is only caused in the plane of excitation.}
\end{figure*}

\begin{figure*}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_v_ranv_slot_1698.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ random excitation V
		\includegraphics[width=1.0\linewidth]{profile_v_ranv_slot_1532.png}
	\end{minipage}
	\caption{\label{fig:ranexpprof}Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the random excitation in V. For both bunches the transverse damper is not active. The distribution changes in the reference bunch (left), here slot 1698, are much less than for the bunch experiencing the maximum excitation (right), here slot 2696.}
      \end{figure*}

\begin{figure*}
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_scale_amp_ranh_lblshort.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_scale_amp_ranv_lblshort.png}
	\end{minipage}	
	\begin{minipage}[t]{0.32\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_scale_amp_ranhv_lblshort.png}
	\end{minipage}	
	\caption{\label{fig:ranexplossplane} Comparison of scaling of loss rates with excitation amplitude for a random excitation only in H (top), only in V (center) and in H+V (bottom) measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars. The loss rate is considerably reduced for the bunches with transverse damper active and is approximately additive with the excitation plane, meaning that double the loss rate is observed for an excitation in H+V compared to only in H or only in V.}
      \end{figure*}

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{2017_scale_amp_7th_ranhv_lblshort.png}
	\caption{\label{fig:ranexploss}  Comparison of scaling of loss rates with excitation amplitude for a random excitation and \seventhtp\ in H+V measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars.}
\end{figure}

>>>>

\begin{figure*}
  \begin{tabular}{cc}
    No excitation & Random excitation, H+V \\
    \includegraphics[width=\fmawidth]{2017injnocolc15o+19_6noerru_dp0_amp.png} &
    \includegraphics[width=\fmawidth]{2017injnocolc15o+19_6noerruranadthv_1nrad_dp0_amp.png} \\
  \end{tabular}
  \caption{FMA in transverse amplitude space without excitation (left)
    and with a random 1-nrad H+V excitation (right), based on the 2017
    injection optics with no lattice errors and tunes (62.27,
    60.295).}
  \label{fig:ran2017fmaamp}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    \includegraphics[width=\halfwidth]{2017injerra2b2u_ranadt_3_5um_intensity.png} &
    \includegraphics[width=\halfwidth]{2017injerra2b2u_ranadt_3_5um_sigm.png}\\
    \includegraphics[width=\halfwidth]{2017injerra2b2u_ranadt_3_5um_emit1.png} &
    \includegraphics[width=\halfwidth]{2017injerra2b2u_ranadt_3_5um_emit2.png}\\
  \end{tabular}
  \caption{Simulations (distribution tracking) based on the 2017
    injection optics with standard lattice errors and
    $(Q_x, Q_y) = (62.27, 60.295)$: relative bunch intensity (top
    left), bunch length (top right), horizontal emittance (bottom
    left), and vertical emittance (bottom right). The solid black line
    indicates the reference case with no excitation. The dashed and
    dotted lines are the results of random excitations (H, V, or H+V)
    with amplitudes 12~nrad and 24~nrad.}
  \label{fig:ransim}
\end{figure*}

\begin{figure*}
  \begin{tabular}{ccc}
    \multicolumn{3}{c}{Random excitation, V} \\
    \includegraphics[width=\thirdwidth]{2017_bunch_intensity_vran_no_damper_avg.png} &
    \includegraphics[width=\thirdwidth]{2017_emith_avg_rel_vran_no_damper.png} &
    \includegraphics[width=\thirdwidth]{2017_emitv_avg_rel_vran_no_damper.png} \\
    \multicolumn{3}{c}{Random excitation, H+V} \\
    \includegraphics[width=\thirdwidth]{2017_bunch_intensity_hvran_no_damper_avg.png} &
    \includegraphics[width=\thirdwidth]{2017_emith_avg_rel_hvran_no_damper.png} &
    \includegraphics[width=\thirdwidth]{2017_emitv_avg_rel_hvran_no_damper.png}\\
  \end{tabular}
  \caption{Measured effects of the random excitation (in V, top row;
    and H+V, bottom row) during the 2017 experiment: relative
    intensity losses (left), relative horizontal emittance (center),
    and relative vertical emittance (right).}
  \label{fig:ranexp}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    Reference bunch, no excitation & Excited bunch, random excitation, V \\
    \includegraphics[width=\bsrtwidth]{profile_v_ranv_slot_1698.png} &
    \includegraphics[width=\bsrtwidth]{profile_v_ranv_slot_1532.png} \\
  \end{tabular}
  \caption{Vertical beam profiles measured with the Beam Synchrotron
    Radiation Telescope (BSRT) during the 2017 experiments. The
    profiles are taken at the end of the random excitation in V. For
    these bunches, the transverse damper was not active. The data are
    presented in the same way as in Fig.~\ref{fig:10thexpprof}. The
    distribution changes in the bunch experiencing the maximum
    excitation (right) were larger than those in the reference bunch
    (left). In both cases, distributions retained a Gaussian shape.}
  \label{fig:ranexpprof}
\end{figure*}

\begin{figure*}
  \begin{tabular}{ccc}
  \includegraphics[width=\thirdwidth]{2017_scale_amp_ranh_lblshort.png} &
  \includegraphics[width=\thirdwidth]{2017_scale_amp_ranv_lblshort.png} &
  \includegraphics[width=\thirdwidth]{2017_scale_amp_ranhv_lblshort.png} \\
  \end{tabular}
  \caption{Measured loss rates as a function of amplitude for random
    excitations in H only (left), V only (center), and H+V
    (right). For each of the three excitation modes, three consecutive
    data sets were taken (black, red, and yellow), with increasing
    maximum amplitude. Data were taken simultaneously with no
    transverse damper on some bunches (filled circles and solid lines)
    and with the damper active on other bunches (empty circles and
    dashed lines). The lines represent empirical second-order
    polynomial fits.}
  \label{fig:ranexplossplane}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2017_scale_amp_7th_ranhv_lblshort.png}
  \caption{Comparison of measured loss rates vs.\ excitation amplitude
    between random and \seventhtp\ in H+V, obtained during the 2017
    experiment.}
  \label{fig:ranexploss}
\end{figure}
